Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-13 Draft.tex

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K and for BSCCO of 110K $\pm$ 9K. 
According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. 
The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. 
While the sample we had was specified for $n=3$, it is quite possible that $n=2$,  with a $T_C$ of 85K, were also present in our sample. \cite{colo} The fluctuations shown in Fig. \ref{BSCCOplot2} could be due to the $n=2$ compound, which stopped superconducting before the $n=3$ transition. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. 
This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.

>>>>

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K (averaged between the two trials) and for BSCCO of 110K $\pm$ 9K. 
According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. 
Our values also agree with those found in the literature, 91 K for YBCO \cite{ybcotemp} and 110 K for $n=3$ BSCCO \cite{temps}.
The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. 
While the sample we had was specified for $n=3$, it is quite possible that $n=2$,  with a $T_C$ of 85K, were also present in our sample. The fluctuations shown in Fig. \ref{BSCCOplot2} could be due to the $n=2$ compound, which stopped superconducting before the $n=3$ transition. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. 
This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.
